<<<<<<< HEAD
---
title: "MGSC 310 Final Project Rough Draft"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
# As long as you are working in a Rstudio Project file, you shouldn't need to 'hard code' directories like this 
# change to your own working directory
# knitr::opts_knit$set(root.dir = 'C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')
# setwd('C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')

# set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)
rm(list = ls())

# general rchunk code options

# this sets text to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')
```

### Importing Libraries
```{r}
library(magrittr)
library('rsample')
library('tidyverse')
library('ISLR')
library('yardstick')
library('ggplot2')
library('plotROC')
library('rsample')
library('glmnet')
library('glmnetUtils')
library('forcats')
library('broom')
```

### Cleaning the dataset 
```{r}
lego_sets <- read.csv("lego_sets.csv")

lego_clean <- lego_sets %>% select(-c(prod_long_desc,theme_name,prod_desc,set_name)) %>% 
  mutate(
  ages = factor(ages),
  review_difficulty = factor(review_difficulty), 
  country = factor(country)
) %>% drop_na()

```

### Inspecting the data set
```{r}
lego_clean

lego_clean %>% glimpse()

summary(lego_clean)


```
```{r}

lego_clean %>% group_by(ages)

ggplot(lego_clean, aes(ages)) + 
  geom_bar() +
  coord_flip()
#should we keep this graph?

```

### Fixing ages

```{r}

table(lego_clean$ages)

```

```{r}

lego_clean <- lego_clean %>% mutate(ages = recode(ages, "10-14" = "10")) %>%
                             mutate(ages = recode(ages, "10-16" = "10")) %>%
                             mutate(ages = recode(ages, "10-21" = "10")) %>%
                             mutate(ages = recode(ages, "10+" = "10")) %>%
                             mutate(ages = recode(ages, "11-16" = "11")) %>%
                             mutate(ages = recode(ages, "12-16" = "12")) %>%
                             mutate(ages = recode(ages, "12+" = "12")) %>%
                             mutate(ages = recode(ages, "14+" = "14")) %>%
                             mutate(ages = recode(ages, "16+" = "16")) %>%
                             mutate(ages = recode(ages, "1½-3" = "1.5")) %>%
                             mutate(ages = recode(ages, "1½-5" = "1.5")) %>%
                             mutate(ages = recode(ages, "2-5" = "2")) %>%
                             mutate(ages = recode(ages, "4-7" = "4")) %>%
                             mutate(ages = recode(ages, "4-99" = "4")) %>%  
                             mutate(ages = recode(ages, "4+" = "4")) %>%
                             mutate(ages = recode(ages, "5-12" = "5")) %>%
                             mutate(ages = recode(ages, "5-8" = "5")) %>%
                             mutate(ages = recode(ages, "5+" = "5")) %>%
                             mutate(ages = recode(ages, "6-12" = "6")) %>%
                             mutate(ages = recode(ages, "6-14" = "6")) %>%
                             mutate(ages = recode(ages, "6+" = "6")) %>%
                             mutate(ages = recode(ages, "7-12" = "7")) %>%
                             mutate(ages = recode(ages, "7-14" = "7")) %>%
                             mutate(ages = recode(ages, "7+" = "7")) %>%
                             mutate(ages = recode(ages, "8-12" = "8")) %>%
                             mutate(ages = recode(ages, "8-14" = "8")) %>%
                             mutate(ages = recode(ages, "8+" = "8")) %>%
                             mutate(ages = recode(ages, "9-12" = "9")) %>%
                             mutate(ages = recode(ages, "9-14" = "9")) %>%
                             mutate(ages = recode(ages, "9-16" = "9")) %>%
                             mutate(ages = recode(ages, "9+" = "9"))
                              
sorted_factors <- paste(sort(as.double(levels(lego_clean$ages))))
lego_clean$ages <- factor(lego_clean$ages, levels = sorted_factors)
lego_clean <-lego_clean %>% rename(minage = ages)

table(lego_clean$minage)

```

### Checking graph again

```{r}

lego_clean %>% group_by(minage)

ggplot(lego_clean, aes(minage)) + 
  geom_bar() +
  coord_flip()

```

### Creating training and testing data sets (working on clustering countries together to help the model perform better by the time we submit our final project)
```{r}

lego_split <- initial_split(lego_clean, p = 0.75)
lego_train <- training(lego_split)
lego_test <- testing(lego_split)

```


### Creating a GLM model
```{r}
glm_mod <- glm(list_price ~ minage + piece_count + num_reviews + play_star_rating + 
                 review_difficulty + star_rating + 
                  val_star_rating + country, 
           data = lego_train)
```

### Generating predictions
```{r}
preds_train_glm <- predict(glm_mod,
                          newdata = lego_train)
```

### Creating a results data frame
```{r}
results_train_glm <- data.frame(
  preds = preds_train_glm,
  true = lego_train$list_price
)
```

### Plotting the true and predicted values
```{r}
ggplot(results_train_glm, 
       aes(x = true, y = preds)) +
  geom_point(alpha = 1/2, size = 4) +
  geom_smooth(color = "red")
```

### Evaluating the metrics
```{r}
metrics(results_train_glm, preds, true)
```

Can we get better error rates with a different model?


### Enet Model
```{r}
enet_mod <- cva.glmnet(list_price ~ minage + piece_count + num_reviews + 
                         play_star_rating + review_difficulty + star_rating + 
                         val_star_rating + country, 
                         data = lego_train,
                       alpha = seq(0,1, by = 0.05))

plot(enet_mod)
```


### Minloss plot to determine Lasso vs. Ridge
```{r}
minlossplot(enet_mod, 
            cv.type = "min")
```

We determine that this is a lasso model because there is the least amount of error when alpha is equal to 1.  This means that only a few of the variables we chose are highly influential to the model.

### Creating the Lasso Model
```{r}
lasso_mod <- cv.glmnet(list_price ~ minage + piece_count + num_reviews + play_star_rating + review_difficulty + star_rating + val_star_rating + country, 
                  data = lego_train,
                  alpha = 1)

plot(lasso_mod)
```
lambda.1se does not increase the mean-squared error much compared to lambda.min.  As such, we would choose the lambda.1se value for lambda in order to increase the shrinkage in our model.

### Which variables are the most influential?
```{r}
library(coefplot)
coefpath(lasso_mod)
```
It appears that the 'ages' variable is the most influential to the model because it shrinks last.




### Generating predictions for lasso
```{r}
preds_train_lasso <- predict(lasso_mod,
                          newdata = lego_train)
```

### Creating a results data frame
```{r}
results_train_lasso <- data.frame(
  preds = preds_train_lasso,
  true = lego_train$list_price
)
```



```{r}
metrics(results_train_lasso, X1, true)
# fix this, for some reason preds is X1

```

```{r}
ggplot(results_train_lasso, 
       aes(x = true, y = X1)) +
  geom_point(alpha = 1/2, size = 4) +
  geom_smooth(color = "red")
```

The graph looks the same?

There are outliers on both graphs, should we talk about those? also, it looksl ike there are some predictions that level off around $400 when the real value is 900.  What could cause this?



```{r}

metrics(results_train_glm, preds, true)

```




=======
---
title: "MGSC 310 Final Project Rough Draft"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
# As long as you are working in a Rstudio Project file, you shouldn't need to 'hard code' directories like this 
# change to your own working directory
# knitr::opts_knit$set(root.dir = 'C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')
# setwd('C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')

# set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)
rm(list = ls())

# general rchunk code options

# this sets text to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')
```

### Importing Libraries
```{r}
library(magrittr)
library('rsample')
library('tidyverse')
library('ISLR')
library('yardstick')
library('ggplot2')
library('plotROC')
library('rsample')
library('glmnet')
library('glmnetUtils')
library('forcats')
library('broom')
```

### Cleaning the dataset 
```{r}
lego_sets <- read.csv("lego_sets.csv")

lego_clean <- lego_sets %>% select(-c(prod_long_desc,theme_name,prod_desc,set_name)) %>% 
  mutate(
  ages = factor(ages),
  review_difficulty = factor(review_difficulty), 
  country = factor(country)
) %>% drop_na()

```

### Inspecting the data set
```{r}
lego_clean

lego_clean %>% glimpse()

summary(lego_clean)


```
```{r}

lego_clean %>% group_by(ages)

ggplot(lego_clean, aes(ages)) + 
  geom_bar() +
  coord_flip()
#should we keep this graph?

```

### Fixing ages

```{r}

table(lego_clean$ages)

```

```{r}

lego_clean <- lego_clean %>% mutate(ages = recode(ages, "10-14" = "10")) %>%
                             mutate(ages = recode(ages, "10-16" = "10")) %>%
                             mutate(ages = recode(ages, "10-21" = "10")) %>%
                             mutate(ages = recode(ages, "10+" = "10")) %>%
                             mutate(ages = recode(ages, "11-16" = "11")) %>%
                             mutate(ages = recode(ages, "12-16" = "12")) %>%
                             mutate(ages = recode(ages, "12+" = "12")) %>%
                             mutate(ages = recode(ages, "14+" = "14")) %>%
                             mutate(ages = recode(ages, "16+" = "16")) %>%
                             mutate(ages = recode(ages, "1½-3" = "1.5")) %>%
                             mutate(ages = recode(ages, "1½-5" = "1.5")) %>%
                             mutate(ages = recode(ages, "2-5" = "2")) %>%
                             mutate(ages = recode(ages, "4-7" = "4")) %>%
                             mutate(ages = recode(ages, "4-99" = "4")) %>%  
                             mutate(ages = recode(ages, "4+" = "4")) %>%
                             mutate(ages = recode(ages, "5-12" = "5")) %>%
                             mutate(ages = recode(ages, "5-8" = "5")) %>%
                             mutate(ages = recode(ages, "5+" = "5")) %>%
                             mutate(ages = recode(ages, "6-12" = "6")) %>%
                             mutate(ages = recode(ages, "6-14" = "6")) %>%
                             mutate(ages = recode(ages, "6+" = "6")) %>%
                             mutate(ages = recode(ages, "7-12" = "7")) %>%
                             mutate(ages = recode(ages, "7-14" = "7")) %>%
                             mutate(ages = recode(ages, "7+" = "7")) %>%
                             mutate(ages = recode(ages, "8-12" = "8")) %>%
                             mutate(ages = recode(ages, "8-14" = "8")) %>%
                             mutate(ages = recode(ages, "8+" = "8")) %>%
                             mutate(ages = recode(ages, "9-12" = "9")) %>%
                             mutate(ages = recode(ages, "9-14" = "9")) %>%
                             mutate(ages = recode(ages, "9-16" = "9")) %>%
                             mutate(ages = recode(ages, "9+" = "9"))
                              
sorted_factors <- paste(sort(as.double(levels(lego_clean$ages))))
lego_clean$ages <- factor(lego_clean$ages, levels = sorted_factors)
lego_clean <-lego_clean %>% rename(minage = ages)

table(lego_clean$minage)

```

### Checking graph again

```{r}

lego_clean %>% group_by(minage)

ggplot(lego_clean, aes(minage)) + 
  geom_bar() +
  coord_flip()

```

### Creating training and testing data sets (working on clustering countries together to help the model perform better by the time we submit our final project)
```{r}

lego_split <- initial_split(lego_clean, p = 0.75)
lego_train <- training(lego_split)
lego_test <- testing(lego_split)

```


### Creating a GLM model
```{r}
glm_mod <- glm(list_price ~ minage + piece_count + num_reviews + play_star_rating + 
                 review_difficulty + star_rating + 
                  val_star_rating + country, 
           data = lego_train)
```

### Generating predictions
```{r}
preds_train_glm <- predict(glm_mod,
                          newdata = lego_train)
```

### Creating a results data frame
```{r}
results_train_glm <- data.frame(
  preds = preds_train_glm,
  true = lego_train$list_price
)
```

### Plotting the true and predicted values
```{r}
ggplot(results_train_glm, 
       aes(x = true, y = preds)) +
  geom_point(alpha = 1/2, size = 4) +
  geom_smooth(color = "red")
```

### Evaluating the metrics
```{r}
metrics(results_train_glm, preds, true)
```

Can we get better error rates with a different model?


### Enet Model
```{r}
enet_mod <- cva.glmnet(list_price ~ minage + piece_count + num_reviews + 
                         play_star_rating + review_difficulty + star_rating + 
                         val_star_rating + country, 
                         data = lego_train,
                       alpha = seq(0,1, by = 0.05))

plot(enet_mod)
```


### Minloss plot to determine Lasso vs. Ridge
```{r}
minlossplot(enet_mod, 
            cv.type = "min")
```

We determine that this is a lasso model because there is the least amount of error when alpha is equal to 1.  This means that only a few of the variables we chose are highly influential to the model.

### Creating the Lasso Model
```{r}
lasso_mod <- cv.glmnet(list_price ~ minage + piece_count + num_reviews + play_star_rating + review_difficulty + star_rating + val_star_rating + country, 
                  data = lego_train,
                  alpha = 1)

plot(lasso_mod)
```
lambda.1se does not increase the mean-squared error much compared to lambda.min.  As such, we would choose the lambda.1se value for lambda in order to increase the shrinkage in our model.

### Which variables are the most influential?
```{r}
library(coefplot)
coefpath(lasso_mod)
```
It appears that the 'ages' variable is the most influential to the model because it shrinks last.




### Generating predictions for lasso
```{r}
preds_train_lasso <- predict(lasso_mod,
                          newdata = lego_train)
```

### Creating a results data frame
```{r}
results_train_lasso <- data.frame(
  preds = preds_train_lasso,
  true = lego_train$list_price
)
```



```{r}
metrics(results_train_lasso, X1, true)
# fix this, for some reason preds is X1

```

```{r}
ggplot(results_train_lasso, 
       aes(x = true, y = X1)) +
  geom_point(alpha = 1/2, size = 4) +
  geom_smooth(color = "red")
```

The graph looks the same?

There are outliers on both graphs, should we talk about those? also, it looksl ike there are some predictions that level off around $400 when the real value is 900.  What could cause this?



```{r}

metrics(results_train_glm, preds, true)

```




>>>>>>> 82db6483d02fd204cf16f5c9506cc817022df89d
